Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-05-06 WSSSPE2_report/WSSSPE2_review.tex
Break down a long sentence.

The review process was fairly standard. First, reviewers bid for papers. Then an
automated system matched the bids to determine assignments. Next, reviewers 
completed their assigned reviews (with an average of 4.9 reviews per paper, and
4.1 reviews per reviewer). This process was done through
EasyChair\footnote{http://easychair.org/}, which allowed reviewers to provide
scores on relevance and comments to the organizers, who used the information to
decide which papers to associate with the workshop and provided the comments to
the authors to help them improve their papers.

>>>>

The review process was fairly standard. First, reviewers bid for papers. Then an
automated system matched the bids to determine assignments. After the reviewers 
completed their assigned reviews (with an average of 4.9 reviews per paper and
4.1 reviews per reviewer), they used
EasyChair\footnote{http://easychair.org/} to record
scores on relevance and comments. Finally, the organizers accessed the information to
decide which papers to associate with the workshop and provided the comments to
the authors to help them improve their papers.
